---
title: 'Meta Analysis: Exploring Results'
subtitle: 'Beadchip'
output: 
    html_document:
        code_folding: "hide"
---
Date 7/28/2021
```{r working directory, warning=F, message=F}
setwd("/Users/Emma/Documents/Bioinformatics/DEG/MetaAnalysisProject_Apr2021")
library(EnhancedVolcano)
```

## GSE8479

- Resistance Exercise Reverses Aging in Human Skeletal Muscle
- geo: https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE8479
- journal: https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0000465
- n = 14 (m6 f8)
- older

```{r GSE8479}
GSE8479F <- read.csv("beadchip/GSE8479/res_GSE8479F.csv", header = T)
GSE8479M <- read.csv("beadchip/GSE8479/res_GSE8479M.csv", header = T)
```


```{r GSE8479F volcano}
EnhancedVolcano(GSE8479F,
                lab = GSE8479F$SYMBOL,
                # selectLab = 'Peptide9A',
                x = 'logFC',
                y = 'adj.P.Val',
                xlim = c(-2,2), ##x軸の範囲
                ylim = c(0, 5),
                xlab = bquote(~Log[2]~ 'fold change'), ##x軸タイトル
                ylab = bquote(~-Log[10]~adjusted~italic(P)),
                pCutoff = 0.05,
                FCcutoff = 0.5,
                pointSize = 2.0, ##図中のドットのサイズ
                labSize = 3.0, ##図中のラベルのサイズ
                col = c('black', 'red', 'orange', 'blue'),
                legendPosition = 'right',
                legendLabels = c('Not Significant','Not Significant, But Big Fold Change',
                           'Signficant, Minimal Fold Change','Signficant, Big Fold Change'),
                legendLabSize = 8, ##ドットの説明文
                legendIconSize = 5.0, ##ラベルのドットサイズ
                labCol = 'black',
                labFace = 'bold') +
  
                labs(title = "GSE8479F", ##一番上のタイトル
                     titleLabSize = 25, ##タイトルのサイズ
                     subtitle = "pre vs post", ##タイトル下のサブタイトル
                     caption = "") ##x軸の下くらいに文字を入れられる

### 特定のgeneを取り出したplot図
# topGene <- rownames(res)[663] #86: 128B, 525: SHMOOSE, 148: Humanin, 663: MOTSc, SHLP6, 644: SHLP2
# plotCounts(dds, topGene, intgroup = c("sarcopenia_status"), xlab = "Group", ylabel = "Normalized Counts") 
```


```{r GSE8479M volcano}
EnhancedVolcano(GSE8479M,
                lab = GSE8479M$SYMBOL,
                # selectLab = 'Peptide9A',
                x = 'logFC',
                y = 'adj.P.Val',
                xlim = c(-2,2), ##x軸の範囲
                ylim = c(0, 3),
                xlab = bquote(~Log[2]~ 'fold change'), ##x軸タイトル
                ylab = bquote(~-Log[10]~adjusted~italic(P)),
                pCutoff = 0.05,
                FCcutoff = 0.5,
                pointSize = 2.0, ##図中のドットのサイズ
                labSize = 3.0, ##図中のラベルのサイズ
                col = c('black', 'red', 'orange', 'blue'),
                legendPosition = 'right',
                legendLabels = c('Not Significant','Not Significant, But Big Fold Change',
                           'Signficant, Minimal Fold Change','Signficant, Big Fold Change'),
                legendLabSize = 8, ##ドットの説明文
                legendIconSize = 5.0, ##ラベルのドットサイズ
                labCol = 'black',
                labFace = 'bold') +
  
                labs(title = "GSE8479M", ##一番上のタイトル
                     titleLabSize = 25, ##タイトルのサイズ
                     subtitle = "pre vs post", ##タイトル下のサブタイトル
                     caption = "") ##x軸の下くらいに文字を入れられる

### 特定のgeneを取り出したplot図
# topGene <- rownames(res)[663] #86: 128B, 525: SHMOOSE, 148: Humanin, 663: MOTSc, SHLP6, 644: SHLP2
# plotCounts(dds, topGene, intgroup = c("sarcopenia_status"), xlab = "Group", ylabel = "Normalized Counts") 

```

<br>

## GSE58249

- GEO: https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE58249
- pubmed: https://pubmed.ncbi.nlm.nih.gov/25138607/
- ncbi full txt: https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4200377/
- resistance (n = 9) / aerobic (n = 8)
- 13 female, 5 male

```{r GSE58249}
GSE58249FA <- read.csv("beadchip/GSE58249/res_GSE58249reFA.csv", header = T)
GSE58249FR <- read.csv("beadchip/GSE58249/res_GSE58249reFR.csv", header = T)
GSE58249MA <- read.csv("beadchip/GSE58249/res_GSE58249reMA.csv", header = T)
GSE58249MR <- read.csv("beadchip/GSE58249/res_GSE58249reMR.csv", header = T)
```


```{r GSE58249FA volcano}
EnhancedVolcano(GSE58249FA,
                lab = GSE58249FA$SYMBOL,
                # selectLab = 'Peptide9A',
                x = 'logFC',
                y = 'adj.P.Val',
                xlim = c(-2,2), ##x軸の範囲
                ylim = c(0, 3),
                xlab = bquote(~Log[2]~ 'fold change'), ##x軸タイトル
                ylab = bquote(~-Log[10]~adjusted~italic(P)),
                pCutoff = 0.05,
                FCcutoff = 0.5,
                pointSize = 2.0, ##図中のドットのサイズ
                labSize = 3.0, ##図中のラベルのサイズ
                col = c('black', 'red', 'orange', 'blue'),
                legendPosition = 'right',
                legendLabels = c('Not Significant','Not Significant, But Big Fold Change',
                           'Signficant, Minimal Fold Change','Signficant, Big Fold Change'),
                legendLabSize = 8, ##ドットの説明文
                legendIconSize = 5.0, ##ラベルのドットサイズ
                labCol = 'black',
                labFace = 'bold') +
  
                labs(title = "GSE58249FA", ##一番上のタイトル
                     titleLabSize = 25, ##タイトルのサイズ
                     subtitle = "pre vs post", ##タイトル下のサブタイトル
                     caption = "") ##x軸の下くらいに文字を入れられる

### 特定のgeneを取り出したplot図
# topGene <- rownames(res)[663] #86: 128B, 525: SHMOOSE, 148: Humanin, 663: MOTSc, SHLP6, 644: SHLP2
# plotCounts(dds, topGene, intgroup = c("sarcopenia_status"), xlab = "Group", ylabel = "Normalized Counts") 
```


```{r GSE58249FR volcano}
EnhancedVolcano(GSE58249FR,
                lab = GSE58249FR$SYMBOL,
                # selectLab = 'Peptide9A',
                x = 'logFC',
                y = 'adj.P.Val',
                xlim = c(-2,2), ##x軸の範囲
                ylim = c(0, 3),
                xlab = bquote(~Log[2]~ 'fold change'), ##x軸タイトル
                ylab = bquote(~-Log[10]~adjusted~italic(P)),
                pCutoff = 0.05,
                FCcutoff = 0.5,
                pointSize = 2.0, ##図中のドットのサイズ
                labSize = 3.0, ##図中のラベルのサイズ
                col = c('black', 'red', 'orange', 'blue'),
                legendPosition = 'right',
                legendLabels = c('Not Significant','Not Significant, But Big Fold Change',
                           'Signficant, Minimal Fold Change','Signficant, Big Fold Change'),
                legendLabSize = 8, ##ドットの説明文
                legendIconSize = 5.0, ##ラベルのドットサイズ
                labCol = 'black',
                labFace = 'bold') +
  
                labs(title = "GSE58249FR", ##一番上のタイトル
                     titleLabSize = 25, ##タイトルのサイズ
                     subtitle = "pre vs post", ##タイトル下のサブタイトル
                     caption = "") ##x軸の下くらいに文字を入れられる

### 特定のgeneを取り出したplot図
# topGene <- rownames(res)[663] #86: 128B, 525: SHMOOSE, 148: Humanin, 663: MOTSc, SHLP6, 644: SHLP2
# plotCounts(dds, topGene, intgroup = c("sarcopenia_status"), xlab = "Group", ylabel = "Normalized Counts") 
```


```{r GSE58249MA volcano}
EnhancedVolcano(GSE58249MA,
                lab = GSE58249MA$SYMBOL,
                # selectLab = 'Peptide9A',
                x = 'logFC',
                y = 'adj.P.Val',
                xlim = c(-2,2), ##x軸の範囲
                ylim = c(0, 3),
                xlab = bquote(~Log[2]~ 'fold change'), ##x軸タイトル
                ylab = bquote(~-Log[10]~adjusted~italic(P)),
                pCutoff = 0.05,
                FCcutoff = 0.5,
                pointSize = 2.0, ##図中のドットのサイズ
                labSize = 3.0, ##図中のラベルのサイズ
                col = c('black', 'red', 'orange', 'blue'),
                legendPosition = 'right',
                legendLabels = c('Not Significant','Not Significant, But Big Fold Change',
                           'Signficant, Minimal Fold Change','Signficant, Big Fold Change'),
                legendLabSize = 8, ##ドットの説明文
                legendIconSize = 5.0, ##ラベルのドットサイズ
                labCol = 'black',
                labFace = 'bold') +
  
                labs(title = "GSE58249MA", ##一番上のタイトル
                     titleLabSize = 25, ##タイトルのサイズ
                     subtitle = "pre vs post", ##タイトル下のサブタイトル
                     caption = "") ##x軸の下くらいに文字を入れられる

### 特定のgeneを取り出したplot図
# topGene <- rownames(res)[663] #86: 128B, 525: SHMOOSE, 148: Humanin, 663: MOTSc, SHLP6, 644: SHLP2
# plotCounts(dds, topGene, intgroup = c("sarcopenia_status"), xlab = "Group", ylabel = "Normalized Counts") 

```


```{r GSE58249MR volcano}
EnhancedVolcano(GSE58249MR,
                lab = GSE58249MR$SYMBOL,
                # selectLab = 'Peptide9A',
                x = 'logFC',
                y = 'P.Value',
                xlim = c(-2,2), ##x軸の範囲
                ylim = c(0, 4),
                xlab = bquote(~Log[2]~ 'fold change'), ##x軸タイトル
                ylab = bquote(~-Log[10]~italic(P)),
                pCutoff = 0.01,
                FCcutoff = 0.5,
                pointSize = 2.0, ##図中のドットのサイズ
                labSize = 3.0, ##図中のラベルのサイズ
                col = c('black', 'red', 'orange', 'blue'),
                legendPosition = 'right',
                legendLabels = c('Not Significant','Not Significant, But Big Fold Change',
                           'Signficant, Minimal Fold Change','Signficant, Big Fold Change'),
                legendLabSize = 8, ##ドットの説明文
                legendIconSize = 5.0, ##ラベルのドットサイズ
                labCol = 'black',
                labFace = 'bold') +
  
                labs(title = "GSE58249MR", ##一番上のタイトル
                     titleLabSize = 25, ##タイトルのサイズ
                     subtitle = "pre vs post", ##タイトル下のサブタイトル
                     caption = "") ##x軸の下くらいに文字を入れられる

### 特定のgeneを取り出したplot図
# topGene <- rownames(res)[663] #86: 128B, 525: SHMOOSE, 148: Humanin, 663: MOTSc, SHLP6, 644: SHLP2
# plotCounts(dds, topGene, intgroup = c("sarcopenia_status"), xlab = "Group", ylabel = "Normalized Counts") 

```

<br>

## GSE139258

- GEO: https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE139258
- journal: https://physoc.onlinelibrary.wiley.com/doi/full/10.14814/phy2.14416
- **method:** performed multiple measurements of mitochondrial capacity both in vivo and ex vivo in lean or overweight individuals. 18-day aerobic exercise training.
- **participants:**  Lean Active (**LA**, n = 7 males) and Lean/Overweight Sedentary (**LOS**, n = 9; n = 3 males). LOS individuals were not engaged in a regular exercise program. LOS individuals engaged in an exercise protocol for 18 days.

```{r GSE139258}
GSE139258F <- read.csv("beadchip/GSE139258/res_GSE139258reF.csv", header = T)
GSE139258M <- read.csv("beadchip/GSE139258/res_GSE139258reM.csv", header = T)
```


```{r GSE139258F volcano}
EnhancedVolcano(GSE139258F,
                lab = GSE139258F$SYMBOL,
                # selectLab = 'Peptide9A',
                x = 'logFC',
                y = 'P.Value',
                xlim = c(-2,2), ##x軸の範囲
                ylim = c(0, 6),
                xlab = bquote(~Log[2]~ 'fold change'), ##x軸タイトル
                ylab = bquote(~-Log[10]~italic(P)),
                pCutoff = 0.01,
                FCcutoff = 0.5,
                pointSize = 2.0, ##図中のドットのサイズ
                labSize = 3.0, ##図中のラベルのサイズ
                col = c('black', 'red', 'orange', 'blue'),
                legendPosition = 'right',
                legendLabels = c('Not Significant','Not Significant, But Big Fold Change',
                           'Signficant, Minimal Fold Change','Signficant, Big Fold Change'),
                legendLabSize = 8, ##ドットの説明文
                legendIconSize = 5.0, ##ラベルのドットサイズ
                labCol = 'black',
                labFace = 'bold') +
  
                labs(title = "GSE139258F", ##一番上のタイトル
                     titleLabSize = 25, ##タイトルのサイズ
                     subtitle = "pre vs post", ##タイトル下のサブタイトル
                     caption = "") ##x軸の下くらいに文字を入れられる

### 特定のgeneを取り出したplot図
# topGene <- rownames(res)[663] #86: 128B, 525: SHMOOSE, 148: Humanin, 663: MOTSc, SHLP6, 644: SHLP2
# plotCounts(dds, topGene, intgroup = c("sarcopenia_status"), xlab = "Group", ylabel = "Normalized Counts") 

```


```{r GSE139258M volcano}
EnhancedVolcano(GSE139258M,
                lab = GSE139258M$SYMBOL,
                # selectLab = 'Peptide9A',
                x = 'logFC',
                y = 'P.Value',
                xlim = c(-2,2), ##x軸の範囲
                ylim = c(0, 4),
                xlab = bquote(~Log[2]~ 'fold change'), ##x軸タイトル
                ylab = bquote(~-Log[10]~italic(P)),
                pCutoff = 0.01,
                FCcutoff = 0.5,
                pointSize = 2.0, ##図中のドットのサイズ
                labSize = 3.0, ##図中のラベルのサイズ
                col = c('black', 'red', 'orange', 'blue'),
                legendPosition = 'right',
                legendLabels = c('Not Significant','Not Significant, But Big Fold Change',
                           'Signficant, Minimal Fold Change','Signficant, Big Fold Change'),
                legendLabSize = 8, ##ドットの説明文
                legendIconSize = 5.0, ##ラベルのドットサイズ
                labCol = 'black',
                labFace = 'bold') +
  
                labs(title = "GSE139258M", ##一番上のタイトル
                     titleLabSize = 25, ##タイトルのサイズ
                     subtitle = "pre vs post", ##タイトル下のサブタイトル
                     caption = "") ##x軸の下くらいに文字を入れられる

### 特定のgeneを取り出したplot図
# topGene <- rownames(res)[663] #86: 128B, 525: SHMOOSE, 148: Humanin, 663: MOTSc, SHLP6, 644: SHLP2
# plotCounts(dds, topGene, intgroup = c("sarcopenia_status"), xlab = "Group", ylabel = "Normalized Counts") 

```



