---
title: 'Meta Analysis: Exploring Results'
subtitle: 'Microarray'
output: 
    html_document:
        code_folding: "hide"
---
Date 7/28/2021
```{r working directory, warning=F, message=F}
setwd("/Users/Emma/Documents/Bioinformatics/DEG/MetaAnalysisProject_Apr2021")
library(EnhancedVolcano)
```

## GSE1295

- GEO: https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE1295
- Journal: https://journals.physiology.org/doi/full/10.1152/japplphysiol.00331.2004
- pubmed: https://pubmed.ncbi.nlm.nih.gov/25138607/
- 3 female and 3 male (all Overweight)
- **biopsy:** 9M later (24h, 96h: 4D, 336h: 14D)  ---> compare: base & 24h (9M later)
- **exercise type:** Aerobics

```{r GSE1295}
GSE1295F <- read.csv("microarray/GSE1295/res_GSE1295reF.csv", header = T)
GSE1295M <- read.csv("microarray/GSE1295/res_GSE1295reM.csv", header = T)
```


```{r GSE1295F volcano}
EnhancedVolcano(GSE1295F,
                lab = GSE1295F$SYMBOL,
                # selectLab = 'Peptide9A',
                x = 'logFC',
                y = 'P.Value',
                xlim = c(-4,4), ##x軸の範囲
                ylim = c(0, 5),
                xlab = bquote(~Log[2]~ 'fold change'), ##x軸タイトル
                ylab = bquote(~-Log[10]~italic(P)),
                pCutoff = 0.01,
                FCcutoff = 0.5,
                pointSize = 2.0, ##図中のドットのサイズ
                labSize = 3.0, ##図中のラベルのサイズ
                col = c('black', 'red', 'orange', 'blue'),
                legendPosition = 'right',
                legendLabels = c('Not Significant','Not Significant, But Big Fold Change',
                           'Signficant, Minimal Fold Change','Signficant, Big Fold Change'),
                legendLabSize = 8, ##ドットの説明文
                legendIconSize = 5.0, ##ラベルのドットサイズ
                labCol = 'black',
                labFace = 'bold') +
  
                labs(title = "GSE1295F", ##一番上のタイトル
                     titleLabSize = 25, ##タイトルのサイズ
                     subtitle = "pre vs post", ##タイトル下のサブタイトル
                     caption = "") ##x軸の下くらいに文字を入れられる

### 特定のgeneを取り出したplot図
# topGene <- rownames(res)[663] #86: 128B, 525: SHMOOSE, 148: Humanin, 663: MOTSc, SHLP6, 644: SHLP2
# plotCounts(dds, topGene, intgroup = c("sarcopenia_status"), xlab = "Group", ylabel = "Normalized Counts") 
```


```{r GSE1295M volcano}
EnhancedVolcano(GSE1295M,
                lab = GSE1295M$SYMBOL,
                # selectLab = 'Peptide9A',
                x = 'logFC',
                y = 'P.Value',
                xlim = c(-3,3), ##x軸の範囲
                ylim = c(0, 4),
                xlab = bquote(~Log[2]~ 'fold change'), ##x軸タイトル
                ylab = bquote(~-Log[10]~italic(P)),
                pCutoff = 0.01,
                FCcutoff = 0.5,
                pointSize = 2.0, ##図中のドットのサイズ
                labSize = 3.0, ##図中のラベルのサイズ
                col = c('black', 'red', 'orange', 'blue'),
                legendPosition = 'right',
                legendLabels = c('Not Significant','Not Significant, But Big Fold Change',
                           'Signficant, Minimal Fold Change','Signficant, Big Fold Change'),
                legendLabSize = 8, ##ドットの説明文
                legendIconSize = 5.0, ##ラベルのドットサイズ
                labCol = 'black',
                labFace = 'bold') +
  
                labs(title = "GSE1295M", ##一番上のタイトル
                     titleLabSize = 25, ##タイトルのサイズ
                     subtitle = "pre vs post", ##タイトル下のサブタイトル
                     caption = "") ##x軸の下くらいに文字を入れられる

### 特定のgeneを取り出したplot図
# topGene <- rownames(res)[663] #86: 128B, 525: SHMOOSE, 148: Humanin, 663: MOTSc, SHLP6, 644: SHLP2
# plotCounts(dds, topGene, intgroup = c("sarcopenia_status"), xlab = "Group", ylabel = "Normalized Counts") 

```

<br>

## GSE28422

- re-analysed by not grouping the age (yng/old), 7/29/2021
- GEO: https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE28422
- pmc: https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3365403/
- 28 young/old adults
    - yng: n=16, 24±1y 8m & 8f
    - old: n=12, 84±1y 6m & 6f
    - male: n=12, female: n=12 (analysed subjects)
- 12 wks of progressive resistance training (3D/wk = 36 sessions)
- biopsies (4): pre, post of 1st & 36th training

```{r GSE28422 pre post}
GSE28422F <- read.csv("microarray/GSE28422/res_GSE28422F.csv", header = T)
GSE28422M <- read.csv("microarray/GSE28422/res_GSE28422M.csv", header = T)
```


```{r GSE28422F adj volcano}
EnhancedVolcano(GSE28422F,
                lab = GSE28422F$SYMBOL,
                # selectLab = 'Peptide9A',
                x = 'logFC',
                y = 'adj.P.Val',
                xlim = c(floor(min(GSE28422F$logFC)), ceiling(max(abs(GSE28422F$logFC)))),
                ylim = c(0, ceiling(max(-log10(GSE28422F$adj.P.Val)))),
                xlab = bquote(~Log[2]~ 'fold change'), ##x軸タイトル
                ylab = bquote(~-Log[10]~adjusted~italic(P)),
                pCutoff = 0.05,
                FCcutoff = 0.5,
                pointSize = 2.0, ##図中のドットのサイズ
                labSize = 3.0, ##図中のラベルのサイズ
                col = c('black', 'red', 'orange', 'blue'),
                legendPosition = 'right',
                legendLabels = c('Not Significant','Not Significant, But Big Fold Change',
                           'Signficant, Minimal Fold Change','Signficant, Big Fold Change'),
                legendLabSize = 8, ##ドットの説明文
                legendIconSize = 5.0, ##ラベルのドットサイズ
                labCol = 'black',
                labFace = 'bold') +
  
                labs(title = "GSE28422F adj.p",
                     titleLabSize = 25,
                     subtitle = "pre vs post",
                     caption = "")

### 特定のgeneを取り出したplot図
# topGene <- rownames(res)[663] #86: 128B, 525: SHMOOSE, 148: Humanin, 663: MOTSc, SHLP6, 644: SHLP2
# plotCounts(dds, topGene, intgroup = c("sarcopenia_status"), xlab = "Group", ylabel = "Normalized Counts") 
```


```{r GSE28422F p volcano}
EnhancedVolcano(GSE28422F,
                lab = GSE28422F$SYMBOL,
                # selectLab = 'Peptide9A',
                x = 'logFC',
                y = 'P.Value',
                xlim = c(floor(min(GSE28422F$logFC)), ceiling(max(abs(GSE28422F$logFC)))),
                ylim = c(0, ceiling(max(-log10(GSE28422F$P.Value)))),
                xlab = bquote(~Log[2]~ 'fold change'), ##x軸タイトル
                ylab = bquote(~-Log[10]~italic(P)),
                pCutoff = 0.01,
                FCcutoff = 0.5,
                pointSize = 2.0, ##図中のドットのサイズ
                labSize = 3.0, ##図中のラベルのサイズ
                col = c('black', 'red', 'orange', 'blue'),
                legendPosition = 'right',
                legendLabels = c('Not Significant','Not Significant, But Big Fold Change',
                           'Signficant, Minimal Fold Change','Signficant, Big Fold Change'),
                legendLabSize = 8, ##ドットの説明文
                legendIconSize = 5.0, ##ラベルのドットサイズ
                labCol = 'black',
                labFace = 'bold') +
  
                labs(title = "GSE28422F p", ##一番上のタイトル
                     titleLabSize = 25, ##タイトルのサイズ
                     subtitle = "pre vs post", ##タイトル下のサブタイトル
                     caption = "") ##x軸の下くらいに文字を入れられる

### 特定のgeneを取り出したplot図
# topGene <- rownames(res)[663] #86: 128B, 525: SHMOOSE, 148: Humanin, 663: MOTSc, SHLP6, 644: SHLP2
# plotCounts(dds, topGene, intgroup = c("sarcopenia_status"), xlab = "Group", ylabel = "Normalized Counts") 
```



```{r GSE28422M adj volcano}
EnhancedVolcano(GSE28422M,
                lab = GSE28422M$SYMBOL,
                # selectLab = 'Peptide9A',
                x = 'logFC',
                y = 'adj.P.Val',
                xlim = c(floor(min(GSE28422M$logFC)), ceiling(max(abs(GSE28422M$logFC)))),
                ylim = c(0, ceiling(max(-log10(GSE28422M$adj.P.Val)))),
                xlab = bquote(~Log[2]~ 'fold change'), ##x軸タイトル
                ylab = bquote(~-Log[10]~adjusted~italic(P)),
                pCutoff = 0.05,
                FCcutoff = 0.5,
                pointSize = 2.0, ##図中のドットのサイズ
                labSize = 3.0, ##図中のラベルのサイズ
                col = c('black', 'red', 'orange', 'blue'),
                legendPosition = 'right',
                legendLabels = c('Not Significant','Not Significant, But Big Fold Change',
                           'Signficant, Minimal Fold Change','Signficant, Big Fold Change'),
                legendLabSize = 8, ##ドットの説明文
                legendIconSize = 5.0, ##ラベルのドットサイズ
                labCol = 'black',
                labFace = 'bold') +
  
                labs(title = "GSE28422M adj.p", ##一番上のタイトル
                     titleLabSize = 25, ##タイトルのサイズ
                     subtitle = "pre vs post", ##タイトル下のサブタイトル
                     caption = "") ##x軸の下くらいに文字を入れられる

### 特定のgeneを取り出したplot図
# topGene <- rownames(res)[663] #86: 128B, 525: SHMOOSE, 148: Humanin, 663: MOTSc, SHLP6, 644: SHLP2
# plotCounts(dds, topGene, intgroup = c("sarcopenia_status"), xlab = "Group", ylabel = "Normalized Counts") 

```


```{r GSE28422M p volcano}
EnhancedVolcano(GSE28422M,
                lab = GSE28422M$SYMBOL,
                # selectLab = 'Peptide9A',
                x = 'logFC',
                y = 'P.Value',
                xlim = c(floor(min(GSE28422M$logFC)), ceiling(max(abs(GSE28422M$logFC)))),
                ylim = c(0, ceiling(max(-log10(GSE28422M$P.Value)))),
                xlab = bquote(~Log[2]~ 'fold change'), ##x軸タイトル
                ylab = bquote(~-Log[10]~italic(P)),
                pCutoff = 0.01,
                FCcutoff = 0.5,
                pointSize = 2.0, ##図中のドットのサイズ
                labSize = 3.0, ##図中のラベルのサイズ
                col = c('black', 'red', 'orange', 'blue'),
                legendPosition = 'right',
                legendLabels = c('Not Significant','Not Significant, But Big Fold Change',
                           'Signficant, Minimal Fold Change','Signficant, Big Fold Change'),
                legendLabSize = 8, ##ドットの説明文
                legendIconSize = 5.0, ##ラベルのドットサイズ
                labCol = 'black',
                labFace = 'bold') +
  
                labs(title = "GSE28422M p", ##一番上のタイトル
                     titleLabSize = 25, ##タイトルのサイズ
                     subtitle = "pre vs post", ##タイトル下のサブタイトル
                     caption = "") ##x軸の下くらいに文字を入れられる

### 特定のgeneを取り出したplot図
# topGene <- rownames(res)[663] #86: 128B, 525: SHMOOSE, 148: Humanin, 663: MOTSc, SHLP6, 644: SHLP2
# plotCounts(dds, topGene, intgroup = c("sarcopenia_status"), xlab = "Group", ylabel = "Normalized Counts") 

```


### GSE28422 (cf. grouped by age)

- GEO: https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE28422
- pmc: https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3365403/
- 28 young/old adults
    - yng: n=16, 24±1y 8m & 8f
    - old: n=12, 84±1y 6m & 6f
    - male: n=14, female: n=14
- 12 wks of progressive resistance training (3D/wk = 36 sessions)
- biopsies (4): pre, post of 1st & 36th training

```{r GSE28422 aged by group}
GSE28422FO <- read.csv("microarray/GSE28422/former_results/res_GSE28422reFO.csv", header = T)
GSE28422FY <- read.csv("microarray/GSE28422/former_results/res_GSE28422reFY.csv", header = T)
GSE28422MO <- read.csv("microarray/GSE28422/former_results/res_GSE28422reMO.csv", header = T)
GSE28422MY <- read.csv("microarray/GSE28422/former_results/res_GSE28422reMY.csv", header = T)
```


```{r GSE28422FO volcano}
EnhancedVolcano(GSE28422FO,
                lab = GSE28422FO$SYMBOL,
                # selectLab = 'Peptide9A',
                x = 'logFC',
                y = 'P.Value',
                xlim = c(-4,4), ##x軸の範囲
                ylim = c(0, 6),
                xlab = bquote(~Log[2]~ 'fold change'), ##x軸タイトル
                ylab = bquote(~-Log[10]~italic(P)),
                pCutoff = 0.01,
                FCcutoff = 0.5,
                pointSize = 2.0, ##図中のドットのサイズ
                labSize = 3.0, ##図中のラベルのサイズ
                col = c('black', 'red', 'orange', 'blue'),
                legendPosition = 'right',
                legendLabels = c('Not Significant','Not Significant, But Big Fold Change',
                           'Signficant, Minimal Fold Change','Signficant, Big Fold Change'),
                legendLabSize = 8, ##ドットの説明文
                legendIconSize = 5.0, ##ラベルのドットサイズ
                labCol = 'black',
                labFace = 'bold') +
  
                labs(title = "GSE28422FO", ##一番上のタイトル
                     titleLabSize = 25, ##タイトルのサイズ
                     subtitle = "pre vs post", ##タイトル下のサブタイトル
                     caption = "") ##x軸の下くらいに文字を入れられる

### 特定のgeneを取り出したplot図
# topGene <- rownames(res)[663] #86: 128B, 525: SHMOOSE, 148: Humanin, 663: MOTSc, SHLP6, 644: SHLP2
# plotCounts(dds, topGene, intgroup = c("sarcopenia_status"), xlab = "Group", ylabel = "Normalized Counts") 
```


```{r GSE28422FY volcano}
EnhancedVolcano(GSE28422FY,
                lab = GSE28422FY$SYMBOL,
                # selectLab = 'Peptide9A',
                x = 'logFC',
                y = 'P.Value',
                # xlim = c(-2,2), ##x軸の範囲
                ylim = c(0, 5),
                xlab = bquote(~Log[2]~ 'fold change'), ##x軸タイトル
                ylab = bquote(~-Log[10]~italic(P)),
                pCutoff = 0.05,
                FCcutoff = 0.5,
                pointSize = 2.0, ##図中のドットのサイズ
                labSize = 3.0, ##図中のラベルのサイズ
                col = c('black', 'red', 'orange', 'blue'),
                legendPosition = 'right',
                legendLabels = c('Not Significant','Not Significant, But Big Fold Change',
                           'Signficant, Minimal Fold Change','Signficant, Big Fold Change'),
                legendLabSize = 8, ##ドットの説明文
                legendIconSize = 5.0, ##ラベルのドットサイズ
                labCol = 'black',
                labFace = 'bold') +
  
                labs(title = "GSE28422FY", ##一番上のタイトル
                     titleLabSize = 25, ##タイトルのサイズ
                     subtitle = "pre vs post", ##タイトル下のサブタイトル
                     caption = "") ##x軸の下くらいに文字を入れられる

### 特定のgeneを取り出したplot図
# topGene <- rownames(res)[663] #86: 128B, 525: SHMOOSE, 148: Humanin, 663: MOTSc, SHLP6, 644: SHLP2
# plotCounts(dds, topGene, intgroup = c("sarcopenia_status"), xlab = "Group", ylabel = "Normalized Counts") 
```



```{r GSE28422MO volcano}
EnhancedVolcano(GSE28422MO,
                lab = GSE28422MO$SYMBOL,
                # selectLab = 'Peptide9A',
                x = 'logFC',
                y = 'P.Value',
                # xlim = c(-2,2), ##x軸の範囲
                ylim = c(0, 5),
                xlab = bquote(~Log[2]~ 'fold change'), ##x軸タイトル
                ylab = bquote(~-Log[10]~italic(P)),
                pCutoff = 0.05,
                FCcutoff = 0.5,
                pointSize = 2.0, ##図中のドットのサイズ
                labSize = 3.0, ##図中のラベルのサイズ
                col = c('black', 'red', 'orange', 'blue'),
                legendPosition = 'right',
                legendLabels = c('Not Significant','Not Significant, But Big Fold Change',
                           'Signficant, Minimal Fold Change','Signficant, Big Fold Change'),
                legendLabSize = 8, ##ドットの説明文
                legendIconSize = 5.0, ##ラベルのドットサイズ
                labCol = 'black',
                labFace = 'bold') +
  
                labs(title = "GSE28422MO", ##一番上のタイトル
                     titleLabSize = 25, ##タイトルのサイズ
                     subtitle = "pre vs post", ##タイトル下のサブタイトル
                     caption = "") ##x軸の下くらいに文字を入れられる

### 特定のgeneを取り出したplot図
# topGene <- rownames(res)[663] #86: 128B, 525: SHMOOSE, 148: Humanin, 663: MOTSc, SHLP6, 644: SHLP2
# plotCounts(dds, topGene, intgroup = c("sarcopenia_status"), xlab = "Group", ylabel = "Normalized Counts") 

```


```{r GSE28422MY volcano}
EnhancedVolcano(GSE28422MY,
                lab = GSE28422MY$SYMBOL,
                # selectLab = 'Peptide9A',
                x = 'logFC',
                y = 'P.Value',
                xlim = c(-4,4), ##x軸の範囲
                ylim = c(0, 5),
                xlab = bquote(~Log[2]~ 'fold change'), ##x軸タイトル
                ylab = bquote(~-Log[10]~italic(P)),
                pCutoff = 0.01,
                FCcutoff = 0.5,
                pointSize = 2.0, ##図中のドットのサイズ
                labSize = 3.0, ##図中のラベルのサイズ
                col = c('black', 'red', 'orange', 'blue'),
                legendPosition = 'right',
                legendLabels = c('Not Significant','Not Significant, But Big Fold Change',
                           'Signficant, Minimal Fold Change','Signficant, Big Fold Change'),
                legendLabSize = 8, ##ドットの説明文
                legendIconSize = 5.0, ##ラベルのドットサイズ
                labCol = 'black',
                labFace = 'bold') +
  
                labs(title = "GSE28422MY", ##一番上のタイトル
                     titleLabSize = 25, ##タイトルのサイズ
                     subtitle = "pre vs post", ##タイトル下のサブタイトル
                     caption = "") ##x軸の下くらいに文字を入れられる

### 特定のgeneを取り出したplot図
# topGene <- rownames(res)[663] #86: 128B, 525: SHMOOSE, 148: Humanin, 663: MOTSc, SHLP6, 644: SHLP2
# plotCounts(dds, topGene, intgroup = c("sarcopenia_status"), xlab = "Group", ylabel = "Normalized Counts") 

```

<br>

## GSE48278

- **journal:** https://link.springer.com/article/10.1007/s00125-014-3343-4
- **GEO:** https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE48278
- A: Mild aerobic exercise - low amount/mod intensity n=10
- B: Inactive control n=10 (**excluded**)
- C: High aerobic exercise - high amt/vig intensity n=10
- D: Moderate aerobic exercise - low amt/vig intensity n=10
- E: Mod aerobic + resistance training n=8
- F: Resistance training only n=9

```{r GSE48278}
GSE48278FA <- read.csv("microarray/GSE48278/res_GSE48278reFA.csv", header = T)
GSE48278FC <- read.csv("microarray/GSE48278/res_GSE48278reFC.csv", header = T)
GSE48278FD <- read.csv("microarray/GSE48278/res_GSE48278reFD.csv", header = T)
GSE48278FE <- read.csv("microarray/GSE48278/res_GSE48278reFE.csv", header = T)
GSE48278FF <- read.csv("microarray/GSE48278/res_GSE48278reFF.csv", header = T)

GSE48278MA <- read.csv("microarray/GSE48278/res_GSE48278reMA.csv", header = T)
GSE48278MC <- read.csv("microarray/GSE48278/res_GSE48278reMC.csv", header = T)
GSE48278MD <- read.csv("microarray/GSE48278/res_GSE48278reMD.csv", header = T)
GSE48278ME <- read.csv("microarray/GSE48278/res_GSE48278reME.csv", header = T)
GSE48278MF <- read.csv("microarray/GSE48278/res_GSE48278reMF.csv", header = T)
```


```{r GSE48278FA volcano}
EnhancedVolcano(GSE48278FA,
                lab = GSE48278FA$SYMBOL,
                # selectLab = 'Peptide9A',
                x = 'logFC',
                y = 'P.Value',
                # xlim = c(-2,2), ##x軸の範囲
                ylim = c(0, 4),
                xlab = bquote(~Log[2]~ 'fold change'), ##x軸タイトル
                ylab = bquote(~-Log[10]~italic(P)),
                pCutoff = 0.01,
                FCcutoff = 0.5,
                pointSize = 2.0, ##図中のドットのサイズ
                labSize = 3.0, ##図中のラベルのサイズ
                col = c('black', 'red', 'orange', 'blue'),
                legendPosition = 'right',
                legendLabels = c('Not Significant','Not Significant, But Big Fold Change',
                           'Signficant, Minimal Fold Change','Signficant, Big Fold Change'),
                legendLabSize = 8, ##ドットの説明文
                legendIconSize = 5.0, ##ラベルのドットサイズ
                labCol = 'black',
                labFace = 'bold') +
  
                labs(title = "GSE48278FA", ##一番上のタイトル
                     titleLabSize = 25, ##タイトルのサイズ
                     subtitle = "pre vs post", ##タイトル下のサブタイトル
                     caption = "") ##x軸の下くらいに文字を入れられる

### 特定のgeneを取り出したplot図
# topGene <- rownames(res)[663] #86: 128B, 525: SHMOOSE, 148: Humanin, 663: MOTSc, SHLP6, 644: SHLP2
# plotCounts(dds, topGene, intgroup = c("sarcopenia_status"), xlab = "Group", ylabel = "Normalized Counts") 

```


```{r GSE48278FC volcano}
EnhancedVolcano(GSE48278FC,
                lab = GSE48278FC$SYMBOL,
                # selectLab = 'Peptide9A',
                x = 'logFC',
                y = 'P.Value',
                # xlim = c(-2,2), ##x軸の範囲
                ylim = c(0, 5),
                xlab = bquote(~Log[2]~ 'fold change'), ##x軸タイトル
                ylab = bquote(~-Log[10]~italic(P)),
                pCutoff = 0.01,
                FCcutoff = 0.5,
                pointSize = 2.0, ##図中のドットのサイズ
                labSize = 3.0, ##図中のラベルのサイズ
                col = c('black', 'red', 'orange', 'blue'),
                legendPosition = 'right',
                legendLabels = c('Not Significant','Not Significant, But Big Fold Change',
                           'Signficant, Minimal Fold Change','Signficant, Big Fold Change'),
                legendLabSize = 8, ##ドットの説明文
                legendIconSize = 5.0, ##ラベルのドットサイズ
                labCol = 'black',
                labFace = 'bold') +
  
                labs(title = "GSE48278FC", ##一番上のタイトル
                     titleLabSize = 25, ##タイトルのサイズ
                     subtitle = "pre vs post", ##タイトル下のサブタイトル
                     caption = "") ##x軸の下くらいに文字を入れられる

### 特定のgeneを取り出したplot図
# topGene <- rownames(res)[663] #86: 128B, 525: SHMOOSE, 148: Humanin, 663: MOTSc, SHLP6, 644: SHLP2
# plotCounts(dds, topGene, intgroup = c("sarcopenia_status"), xlab = "Group", ylabel = "Normalized Counts") 

```


```{r GSE48278FD volcano}
EnhancedVolcano(GSE48278FD,
                lab = GSE48278FD$SYMBOL,
                # selectLab = 'Peptide9A',
                x = 'logFC',
                y = 'P.Value',
                # xlim = c(-2,2), ##x軸の範囲
                ylim = c(0, 6),
                xlab = bquote(~Log[2]~ 'fold change'), ##x軸タイトル
                ylab = bquote(~-Log[10]~italic(P)),
                pCutoff = 0.01,
                FCcutoff = 0.5,
                pointSize = 2.0, ##図中のドットのサイズ
                labSize = 3.0, ##図中のラベルのサイズ
                col = c('black', 'red', 'orange', 'blue'),
                legendPosition = 'right',
                legendLabels = c('Not Significant','Not Significant, But Big Fold Change',
                           'Signficant, Minimal Fold Change','Signficant, Big Fold Change'),
                legendLabSize = 8, ##ドットの説明文
                legendIconSize = 5.0, ##ラベルのドットサイズ
                labCol = 'black',
                labFace = 'bold') +
  
                labs(title = "GSE48278FD", ##一番上のタイトル
                     titleLabSize = 25, ##タイトルのサイズ
                     subtitle = "pre vs post", ##タイトル下のサブタイトル
                     caption = "") ##x軸の下くらいに文字を入れられる

### 特定のgeneを取り出したplot図
# topGene <- rownames(res)[663] #86: 128B, 525: SHMOOSE, 148: Humanin, 663: MOTSc, SHLP6, 644: SHLP2
# plotCounts(dds, topGene, intgroup = c("sarcopenia_status"), xlab = "Group", ylabel = "Normalized Counts") 

```


```{r GSE48278FE volcano}
EnhancedVolcano(GSE48278FE,
                lab = GSE48278FE$SYMBOL,
                # selectLab = 'Peptide9A',
                x = 'logFC',
                y = 'P.Value',
                # xlim = c(-2,2), ##x軸の範囲
                ylim = c(0, 6),
                xlab = bquote(~Log[2]~ 'fold change'), ##x軸タイトル
                ylab = bquote(~-Log[10]~italic(P)),
                pCutoff = 0.01,
                FCcutoff = 0.5,
                pointSize = 2.0, ##図中のドットのサイズ
                labSize = 3.0, ##図中のラベルのサイズ
                col = c('black', 'red', 'orange', 'blue'),
                legendPosition = 'right',
                legendLabels = c('Not Significant','Not Significant, But Big Fold Change',
                           'Signficant, Minimal Fold Change','Signficant, Big Fold Change'),
                legendLabSize = 8, ##ドットの説明文
                legendIconSize = 5.0, ##ラベルのドットサイズ
                labCol = 'black',
                labFace = 'bold') +
  
                labs(title = "GSE48278FE", ##一番上のタイトル
                     titleLabSize = 25, ##タイトルのサイズ
                     subtitle = "pre vs post", ##タイトル下のサブタイトル
                     caption = "") ##x軸の下くらいに文字を入れられる

### 特定のgeneを取り出したplot図
# topGene <- rownames(res)[663] #86: 128B, 525: SHMOOSE, 148: Humanin, 663: MOTSc, SHLP6, 644: SHLP2
# plotCounts(dds, topGene, intgroup = c("sarcopenia_status"), xlab = "Group", ylabel = "Normalized Counts") 

```

```{r GSE48278FF volcano}
EnhancedVolcano(GSE48278FF,
                lab = GSE48278FF$SYMBOL,
                # selectLab = 'Peptide9A',
                x = 'logFC',
                y = 'P.Value',
                # xlim = c(-2,2), ##x軸の範囲
                ylim = c(0, 4),
                xlab = bquote(~Log[2]~ 'fold change'), ##x軸タイトル
                ylab = bquote(~-Log[10]~italic(P)),
                pCutoff = 0.01,
                FCcutoff = 0.5,
                pointSize = 2.0, ##図中のドットのサイズ
                labSize = 3.0, ##図中のラベルのサイズ
                col = c('black', 'red', 'orange', 'blue'),
                legendPosition = 'right',
                legendLabels = c('Not Significant','Not Significant, But Big Fold Change',
                           'Signficant, Minimal Fold Change','Signficant, Big Fold Change'),
                legendLabSize = 8, ##ドットの説明文
                legendIconSize = 5.0, ##ラベルのドットサイズ
                labCol = 'black',
                labFace = 'bold') +
  
                labs(title = "GSE48278FF", ##一番上のタイトル
                     titleLabSize = 25, ##タイトルのサイズ
                     subtitle = "pre vs post", ##タイトル下のサブタイトル
                     caption = "") ##x軸の下くらいに文字を入れられる

### 特定のgeneを取り出したplot図
# topGene <- rownames(res)[663] #86: 128B, 525: SHMOOSE, 148: Humanin, 663: MOTSc, SHLP6, 644: SHLP2
# plotCounts(dds, topGene, intgroup = c("sarcopenia_status"), xlab = "Group", ylabel = "Normalized Counts") 

```


```{r GSE48278MA volcano}
EnhancedVolcano(GSE48278MA,
                lab = GSE48278MA$SYMBOL,
                # selectLab = 'Peptide9A',
                x = 'logFC',
                y = 'P.Value',
                # xlim = c(-2,2), ##x軸の範囲
                ylim = c(0, 4),
                xlab = bquote(~Log[2]~ 'fold change'), ##x軸タイトル
                ylab = bquote(~-Log[10]~italic(P)),
                pCutoff = 0.01,
                FCcutoff = 0.5,
                pointSize = 2.0, ##図中のドットのサイズ
                labSize = 3.0, ##図中のラベルのサイズ
                col = c('black', 'red', 'orange', 'blue'),
                legendPosition = 'right',
                legendLabels = c('Not Significant','Not Significant, But Big Fold Change',
                           'Signficant, Minimal Fold Change','Signficant, Big Fold Change'),
                legendLabSize = 8, ##ドットの説明文
                legendIconSize = 5.0, ##ラベルのドットサイズ
                labCol = 'black',
                labFace = 'bold') +
  
                labs(title = "GSE48278MA", ##一番上のタイトル
                     titleLabSize = 25, ##タイトルのサイズ
                     subtitle = "pre vs post", ##タイトル下のサブタイトル
                     caption = "") ##x軸の下くらいに文字を入れられる

### 特定のgeneを取り出したplot図
# topGene <- rownames(res)[663] #86: 128B, 525: SHMOOSE, 148: Humanin, 663: MOTSc, SHLP6, 644: SHLP2
# plotCounts(dds, topGene, intgroup = c("sarcopenia_status"), xlab = "Group", ylabel = "Normalized Counts") 
```

```{r GSE48278MC volcano}
EnhancedVolcano(GSE48278MC,
                lab = GSE48278MC$SYMBOL,
                # selectLab = 'Peptide9A',
                x = 'logFC',
                y = 'P.Value',
                # xlim = c(-2,2), ##x軸の範囲
                ylim = c(0, 4),
                xlab = bquote(~Log[2]~ 'fold change'), ##x軸タイトル
                ylab = bquote(~-Log[10]~italic(P)),
                pCutoff = 0.01,
                FCcutoff = 0.5,
                pointSize = 2.0, ##図中のドットのサイズ
                labSize = 3.0, ##図中のラベルのサイズ
                col = c('black', 'red', 'orange', 'blue'),
                legendPosition = 'right',
                legendLabels = c('Not Significant','Not Significant, But Big Fold Change',
                           'Signficant, Minimal Fold Change','Signficant, Big Fold Change'),
                legendLabSize = 8, ##ドットの説明文
                legendIconSize = 5.0, ##ラベルのドットサイズ
                labCol = 'black',
                labFace = 'bold') +
  
                labs(title = "GSE48278MC", ##一番上のタイトル
                     titleLabSize = 25, ##タイトルのサイズ
                     subtitle = "pre vs post", ##タイトル下のサブタイトル
                     caption = "") ##x軸の下くらいに文字を入れられる

### 特定のgeneを取り出したplot図
# topGene <- rownames(res)[663] #86: 128B, 525: SHMOOSE, 148: Humanin, 663: MOTSc, SHLP6, 644: SHLP2
# plotCounts(dds, topGene, intgroup = c("sarcopenia_status"), xlab = "Group", ylabel = "Normalized Counts") 
```

```{r GSE48278MD volcano}
EnhancedVolcano(GSE48278MD,
                lab = GSE48278MD$SYMBOL,
                # selectLab = 'Peptide9A',
                x = 'logFC',
                y = 'P.Value',
                # xlim = c(-2,2), ##x軸の範囲
                ylim = c(0, 4),
                xlab = bquote(~Log[2]~ 'fold change'), ##x軸タイトル
                ylab = bquote(~-Log[10]~italic(P)),
                pCutoff = 0.01,
                FCcutoff = 0.5,
                pointSize = 2.0, ##図中のドットのサイズ
                labSize = 3.0, ##図中のラベルのサイズ
                col = c('black', 'red', 'orange', 'blue'),
                legendPosition = 'right',
                legendLabels = c('Not Significant','Not Significant, But Big Fold Change',
                           'Signficant, Minimal Fold Change','Signficant, Big Fold Change'),
                legendLabSize = 8, ##ドットの説明文
                legendIconSize = 5.0, ##ラベルのドットサイズ
                labCol = 'black',
                labFace = 'bold') +
  
                labs(title = "GSE48278MD", ##一番上のタイトル
                     titleLabSize = 25, ##タイトルのサイズ
                     subtitle = "pre vs post", ##タイトル下のサブタイトル
                     caption = "") ##x軸の下くらいに文字を入れられる

### 特定のgeneを取り出したplot図
# topGene <- rownames(res)[663] #86: 128B, 525: SHMOOSE, 148: Humanin, 663: MOTSc, SHLP6, 644: SHLP2
# plotCounts(dds, topGene, intgroup = c("sarcopenia_status"), xlab = "Group", ylabel = "Normalized Counts") 
```

```{r GSE48278ME volcano}
EnhancedVolcano(GSE48278ME,
                lab = GSE48278ME$SYMBOL,
                # selectLab = 'Peptide9A',
                x = 'logFC',
                y = 'P.Value',
                # xlim = c(-2,2), ##x軸の範囲
                ylim = c(0, 5),
                xlab = bquote(~Log[2]~ 'fold change'), ##x軸タイトル
                ylab = bquote(~-Log[10]~italic(P)),
                pCutoff = 0.01,
                FCcutoff = 0.5,
                pointSize = 2.0, ##図中のドットのサイズ
                labSize = 3.0, ##図中のラベルのサイズ
                col = c('black', 'red', 'orange', 'blue'),
                legendPosition = 'right',
                legendLabels = c('Not Significant','Not Significant, But Big Fold Change',
                           'Signficant, Minimal Fold Change','Signficant, Big Fold Change'),
                legendLabSize = 8, ##ドットの説明文
                legendIconSize = 5.0, ##ラベルのドットサイズ
                labCol = 'black',
                labFace = 'bold') +
  
                labs(title = "GSE48278ME", ##一番上のタイトル
                     titleLabSize = 25, ##タイトルのサイズ
                     subtitle = "pre vs post", ##タイトル下のサブタイトル
                     caption = "") ##x軸の下くらいに文字を入れられる

### 特定のgeneを取り出したplot図
# topGene <- rownames(res)[663] #86: 128B, 525: SHMOOSE, 148: Humanin, 663: MOTSc, SHLP6, 644: SHLP2
# plotCounts(dds, topGene, intgroup = c("sarcopenia_status"), xlab = "Group", ylabel = "Normalized Counts") 
```


```{r GSE48278MF volcano}
EnhancedVolcano(GSE48278MF,
                lab = GSE48278MF$SYMBOL,
                # selectLab = 'Peptide9A',
                x = 'logFC',
                y = 'P.Value',
                # xlim = c(-2,2), ##x軸の範囲
                ylim = c(0, 4),
                xlab = bquote(~Log[2]~ 'fold change'), ##x軸タイトル
                ylab = bquote(~-Log[10]~italic(P)),
                pCutoff = 0.01,
                FCcutoff = 0.5,
                pointSize = 2.0, ##図中のドットのサイズ
                labSize = 3.0, ##図中のラベルのサイズ
                col = c('black', 'red', 'orange', 'blue'),
                legendPosition = 'right',
                legendLabels = c('Not Significant','Not Significant, But Big Fold Change',
                           'Signficant, Minimal Fold Change','Signficant, Big Fold Change'),
                legendLabSize = 8, ##ドットの説明文
                legendIconSize = 5.0, ##ラベルのドットサイズ
                labCol = 'black',
                labFace = 'bold') +
  
                labs(title = "GSE48278MF", ##一番上のタイトル
                     titleLabSize = 25, ##タイトルのサイズ
                     subtitle = "pre vs post", ##タイトル下のサブタイトル
                     caption = "") ##x軸の下くらいに文字を入れられる

### 特定のgeneを取り出したplot図
# topGene <- rownames(res)[663] #86: 128B, 525: SHMOOSE, 148: Humanin, 663: MOTSc, SHLP6, 644: SHLP2
# plotCounts(dds, topGene, intgroup = c("sarcopenia_status"), xlab = "Group", ylabel = "Normalized Counts") 
```

<br>

## GSE117525

- Expression of protocadherin gamma in skeletal muscle tissue is associated with
- age and muscle weakness
- **journal:** https://onlinelibrary.wiley.com/doi/full/10.1002/jcsm.12099
- **GEO:** https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE117525
- **pubmed(abst):** https://pubmed.ncbi.nlm.nih.gov/27239416/
- frail old: 31(m24/f6), healthy old: 41(m27/f5)
- MF13, FF16, MH30, FH11: analysied  ---> **unpaied samples were included** (pre: placebo, post: protein)  

```{r GSE117525}
GSE117525F <- read.csv("microarray/GSE117525/res_GSE117525F.csv", header = T)
GSE117525M <- read.csv("microarray/GSE117525/res_GSE117525M.csv", header = T)
```


```{r GSE117525F volcano}
EnhancedVolcano(GSE117525F,
                lab = GSE117525F$SYMBOL,
                # selectLab = 'Peptide9A',
                x = 'logFC',
                y = 'adj.P.Val',
                xlim = c(-1.5,1.5), ##x軸の範囲
                ylim = c(0, 6),
                xlab = bquote(~Log[2]~ 'fold change'), ##x軸タイトル
                ylab = bquote(~-Log[10]~adjusted~italic(P)),
                pCutoff = 0.05,
                FCcutoff = 0.5,
                pointSize = 2.0, ##図中のドットのサイズ
                labSize = 3.0, ##図中のラベルのサイズ
                col = c('black', 'red', 'orange', 'blue'),
                legendPosition = 'right',
                legendLabels = c('Not Significant','Not Significant, But Big Fold Change',
                                 'Signficant, Minimal Fold Change','Signficant, Big Fold Change'),
                legendLabSize = 8, ##ドットの説明文
                legendIconSize = 5.0, ##ラベルのドットサイズ
                labCol = 'black',
                labFace = 'bold') +
    
    labs(title = "GSE117525F", ##一番上のタイトル
         titleLabSize = 25, ##タイトルのサイズ
         subtitle = "pre vs post", ##タイトル下のサブタイトル
         caption = "") ##x軸の下くらいに文字を入れられる

### 特定のgeneを取り出したplot図
# topGene <- rownames(res)[663] #86: 128B, 525: SHMOOSE, 148: Humanin, 663: MOTSc, SHLP6, 644: SHLP2
# plotCounts(dds, topGene, intgroup = c("sarcopenia_status"), xlab = "Group", ylabel = "Normalized Counts") 
```

```{r GSE117525M volcano}
EnhancedVolcano(GSE117525M,
                lab = GSE117525M$SYMBOL,
                # selectLab = 'Peptide9A',
                x = 'logFC',
                y = 'adj.P.Val',
                xlim = c(-1.5,1.5), ##x軸の範囲
                ylim = c(0, 3),
                xlab = bquote(~Log[2]~ 'fold change'), ##x軸タイトル
                ylab = bquote(~-Log[10]~adjusted~italic(P)),
                pCutoff = 0.05,
                FCcutoff = 0.5,
                pointSize = 2.0, ##図中のドットのサイズ
                labSize = 3.0, ##図中のラベルのサイズ
                col = c('black', 'red', 'orange', 'blue'),
                legendPosition = 'right',
                legendLabels = c('Not Significant','Not Significant, But Big Fold Change',
                                 'Signficant, Minimal Fold Change','Signficant, Big Fold Change'),
                legendLabSize = 8, ##ドットの説明文
                legendIconSize = 5.0, ##ラベルのドットサイズ
                labCol = 'black',
                labFace = 'bold') +
    
    labs(title = "GSE117525M", ##一番上のタイトル
         titleLabSize = 25, ##タイトルのサイズ
         subtitle = "pre vs post", ##タイトル下のサブタイトル
         caption = "") ##x軸の下くらいに文字を入れられる

### 特定のgeneを取り出したplot図
# topGene <- rownames(res)[663] #86: 128B, 525: SHMOOSE, 148: Humanin, 663: MOTSc, SHLP6, 644: SHLP2
# plotCounts(dds, topGene, intgroup = c("sarcopenia_status"), xlab = "Group", ylabel = "Normalized Counts") 
```


